---
title: "learn-maatrenutils"
author: "QiaoHang"
format: html
editor: visual
---

# 加载包

```{r}
library(maartenutils)
```

# 列出maartenutils的全部函数

```{r}
ls("package:maartenutils")
```

# Utilities and Miscellaneous Functions

# \`%\|\|%\`

```{r}
# `%||%`
`%||%` <- function(a, b) if (is.null(a) || is.na(a) || length(a) == 0) b else a


```

`%||%` Function Documentation:

## Description

The `%||%` function returns the first argument if it is not NULL, NA, or an empty vector; otherwise, it returns the second argument.

## Usage

``` r
a %||% b
```

## Arguments

-   `a`: an R object.
-   `b`: an R object.

## Details

If `a` is NULL, NA, or an empty vector, the function returns `b`; otherwise, it returns `a`.

## Value

The result of the function is either `a` or `b`, depending on the conditions described in the "Details" section.

## Examples

```{r}
x <- 1
y <- NULL
z <- c()

x_result <- x %||% 10
y_result <- y %||% 10
z_result <- z %||% 10

x_result

# Output: [1] 1 

y_result
# Output: [1] 10

z_result
# Output: [1] 10
```

## See Also

Other functions that can be used for similar purposes include `ifelse`, `coalesce` (from the `dplyr` package), and the `||` and `&&` operators.

Hope this helps! Let me know if you have further questions or issues!
